---
title: "Towards a `future` for R"
subtitle: "A fresh approach to Parallel Computing"
author: "[Nima Hejazi](http://nimahejazi.org)"
date: "`r lubridate::now()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "custom.css"]
    nature:
      highlightStyle: zenburn
      highlightLines: true
      countIncrementalSlides: false
---

```{r knitr_setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 4.5, dpi = 300,
                      fig.cap = "", fig.align = "center")
showtext::showtext.opts(dpi = 300)
```

# Accessing these slides

--

### View online:

* shortened URL: [https://goo.gl/T47hs6](https://goo.gl/T47hs6)

--

### Build locally:

_You'll need to clone the `git` repo of source materials and then build the
slide deck (HTML)._

```{bash, eval=FALSE}
git clone https://github.com/nhejazi/talk_futuRe-intro.git
make
```

???

- This talk will focus on introducing the new `sl3` R package, which provides a
modern implementation of the Super Learner algorithm [@vdl2007super], a method
for performing stacked regressions [@breiman1996stacked] and combining this with
covariate screening and cross-validation.

---
class: inverse, center, middle

# `sl3`: The Core Design

---

# `sl3` Architecture

All of the classes defined in `sl3` are based on the R6 framework, which brings
an object-oriented paradigm to the R language.

## Core classes

- `task` - an object containing the data set of interest and specifying
important features of the data (e.g., repeated measures).

--

- `lrnr_base` - a base class that serves as the foundation for other classes
defined within `sl3`.

--

- `Pipeline` - a learner-type object created by chaining together screening and
learning algorithms, allowing for covariate screening and model fitting to be
subjected to the same cross-validation process.

--

- `Stack` - a stacked regression model -- that is, a learner-type object created
by combining different (independent) learners or pipelines.

???

- Probably good to point out that cross-validating a `Stack` allows for an
included `Pipeline` to be subjected to CV in the same way as other learners
(seriously awesome feature).

---
class: inverse, center, middle

# `sl3` in Action

## There ain't nothin' like a test drive...

---

# Get the package

- Currently, installation from the `master` branch is the only option:

```{r install_pkg, message=FALSE, eval=FALSE}
if (!("sl3" %in% installed.packages())) {
  devtools::install_github("jeremyrcoyle/sl3")
}
```

--

- Work is underway to set up a [`drat`
archive](http://dirk.eddelbuettel.com/code/drat.html) to host all stable
versions of the package.

--

- Of course, the package will eventually be available on CRAN, though a
submission to this repository is still far down the road.

--

To start using `sl3`, let's load the package:

```{r prelims-pkg, message=FALSE}
library(future)
library(future.batchtools)
library(doFuture)
library(BiocParallel.FutureParam)
```

---

# A "toy" data set

We can't do any model fitting without data. We'll use the `cpp` data set,
included with the package, for our experiment.

```{r prelims-data, message=FALSE}
# load example data set
```

???

- A working implementation of a targeted learning approach to biomarker
discovery using moderated statistics.

- Next, we'll walk through analyzing some data.

---

# Setting up a `Task`

Recall that a `Task` is the core structure that holds the data set and
specifications to be respected in the estimation/modeling procedure.

```{r sl3-task-setup, message=FALSE}
```

--

Data is in the nodes:

```{r sl3-task-nodes, message=FALSE}
```

???

- talk about tasks

---

# Screeners, learners, pipelines

Both screeners and learners can be easily instantiated by calling their `new`
methods:

```{r sl3-core-1, message=FALSE}
```

--

We can even pull screening and learning algorithms directly from
`Super Learner`:

```{r sl3-core-2, message=FALSE}
```

--

And pipelines can be easily created by stringing screeners and learners
together:

```{r sl3-core-3, message=FALSE}
```

--

Training a learners (or pipelines) is as easy as calling the `train` method:

```{r sl3-core-4, message=FALSE}
```

---

# Stacks

We can create stacked regression models (Super Learners) by instantiating a new
stack with several existing learners. (Note that we can even incldue pipelines
in the model stack).

```{r sl3-stacks-1, message=FALSE}
```

--

Let's take a look at the predictions made by the stacked model:

```{r sl3-stacks-2, message=FALSE}
```

???

- ...

---

# But What About Cross-Validation?

Almost forgot! CV is necessary in order to honestly evaluate our models and
avoid overfitting. Thus, we need to be able to easily cross-validate the whole
process. We provide facilities for easily doing this, based on the [`origami`
package](https://github.com/jeremyrcoyle/origami).

--

Cross-validating a stacked model is as easy as instantiating and training a new
`Lrnr_cv`. Let's do this with the stacked model we created before

```{r sl3-cv-1, message=FALSE}
```

---

# Putting it all together: Super Learning

We can build a Super Learner model by combining a cross-validated stacked model
with a meta-learning algorithm.

Let's do this with the cross-validated stack we just created, using a GLM as our
meta-learner:

```{r sl3-cv-sl-1, message=FALSE}
```

--

Just as in the cases we've already seen, training the Super Learner is an
essentially trivial process:

```{r sl3-cv-sl-2, message=FALSE}
```

--

What do the predictions from our new Super Learner look like?

```{r sl3-cv-sl-3, message=FALSE}
```

???

- Worth mentioning that the flexibility offered by our design allows us to
invoke the Super Learner algorithm, but we can also do a lot more...

---
class: center, middle

# Thanks!

twitter/[@nshejazi](https://twitter.com/nshejazi), github/[@nhejazi](https://github.com/nhejazi)

[nimahejazi.org](http://nimahejazi.org/), [stat.berkeley.edu/~nhejazi](https://www.stat.berkeley.edu/~nhejazi/)

Slides created via the R package
[**xaringan**](https://github.com/yihui/xaringan).

Powered by [remark.js](https://remarkjs.com),
[**knitr**](http://yihui.name/knitr), and
[R Markdown](https://rmarkdown.rstudio.com).
